---
title: "BLE LTER Stations"
author: "Christina Bonsell"
date: "November 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=F, message=F, warnings=F}
library(leaflet)
library(tidyverse)
```

```{r load,echo=F, message=F, warnings=F}
Stations <- read_csv("BLE_LTER_CP_Stations.csv", 
                     col_types=cols(
  StationId = col_character(),
  StationName = col_character(),
  Latitude = col_double(),
  Longitude = col_double(),
  Habitat = col_character(),
  Type = col_factor()
)) %>% 
  filter(Type!="ocean")

pal <- colorFactor(c("gold", "navy", "chartreuse3"), domain = c("primary", "secondary", "river"))
```
# Zoom in and screenshot for node-based maps
```{r zoom, echo=F, message=F, warnings=F, fig.height=7, fig.width=10}

Stations %>% leaflet() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(~ Longitude, ~ Latitude, 
                   color = ~pal(Type),
                   radius=6,
                   stroke = FALSE, 
                   fillOpacity = 0.5,
                   label= ~StationId,
                   labelOptions = labelOptions(noHide = T,
                                               direction = 'right',
                                               offset=c(0,-5),
                                               opacity=1,
                                               style = list(
                                                 "font-style" = "bold",
                                                 "font-size" = "20px",
                                                 "color"="white",
                                                 "background"="transparent",
                                                 "border"="none",
                                                 "box-shadow"="none"))) %>% 
  addScaleBar() %>% 
  addLegend(pal = pal, values = ~Type, opacity = 1, title="Station type") %>% 
  addMiniMap(zoomLevelFixed = 2, 
             centerFixed=c(65, -150))


```


# Hidden labels
## (Zoom in and screenshot for node-based maps)
```{r nolab, echo=F, message=F, warnings=F, fig.height=6, fig.width=10}

Stations %>% leaflet() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(~ Longitude, ~ Latitude, 
                   color = ~pal(Type),
                   radius=6,
                   stroke = FALSE, 
                   fillOpacity = 0.5,
                   label= ~StationId) %>% 
  addScaleBar() %>% 
  addLegend(pal = pal, values = ~Type, opacity = 1, title="Station type") %>% 
  addMiniMap(zoomLevelFixed = 2, 
             centerFixed=c(65, -150))


```

#Primary and river only
##(zoom in and screenshot for node-based maps)
```{r zoom2, echo=F, message=F, warnings=F, fig.height=7, fig.width=10}
Stations %>% 
  filter(Type!="secondary") %>% 
  leaflet() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(~ Longitude, ~ Latitude, 
                   color = ~pal(Type),
                   radius=6,
                   stroke = FALSE, 
                   fillOpacity = 0.5,
                   label= ~StationId,
                   labelOptions = labelOptions(noHide = T,
                                               direction = 'right',
                                               offset=c(0,-5),
                                              opacity=1,
                                               style = list(
                                                 "font-style" = "bold",
                                                 "font-size" = "20px",
                                                 "color"="white",
                                                 "background"="transparent",
                                                 "border"="none",
                                                 "box-shadow"="none"))) %>% 
  addScaleBar() %>% 
  addLegend(pal = pal, values = ~Type, opacity = 1, title="Station type") %>% 
  addMiniMap(zoomLevelFixed = 2, 
             centerFixed=c(65, -150))

```

#Primary only
##(zoom in and screenshot for node-based maps)

```{r zoom3, echo=F, message=F, warnings=F, fig.height=5, fig.width=10}
Stations %>% 
  filter(Type=="primary") %>% 
  leaflet() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(~ Longitude, ~ Latitude, 
                   color = ~pal(Type),
                   radius=6,
                   stroke = FALSE, 
                   fillOpacity = 0.5,
                   label= ~StationId,
                   labelOptions = labelOptions(noHide = T,
                                               direction = 'right',
                                               offset=c(0,-5),
                                              opacity=1,
                                               style = list(
                                                 "font-style" = "bold",
                                                 "font-size" = "20px",
                                                 "color"="white",
                                                 "background"="transparent",
                                                 "border"="none",
                                                 "box-shadow"="none"))) %>% 
  addScaleBar() %>% 
  addMiniMap(zoomLevelFixed = 2, 
             centerFixed=c(65, -150))

```

#Lagoons (primary+secondary) only
##(zoom in and screenshot for node-based maps)

```{r zoom4, echo=F, message=F, warnings=F, fig.height=5, fig.width=10}
Stations %>% 
  filter(Type!="river") %>% 
  leaflet() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(~ Longitude, ~ Latitude, 
                   color = ~pal(Type),
                   radius=6,
                   stroke = FALSE, 
                   fillOpacity = 0.5,
                   label= ~StationId,
                   labelOptions = labelOptions(noHide = T,
                                               direction = 'right',
                                               offset=c(0,-5),
                                              opacity=1,
                                               style = list(
                                                 "font-style" = "bold",
                                                 "font-size" = "20px",
                                                 "color"="white",
                                                 "background"="transparent",
                                                 "border"="none",
                                                 "box-shadow"="none"))) %>% 
  addScaleBar() %>% 
  addMiniMap(zoomLevelFixed = 2, 
             centerFixed=c(65, -150))

```

#Lagoons

```{r nodes, echo=F, message=F, warnings=F, fig.height=5, fig.width=10}

Nodes <- read_csv("BLE_LTER_Nodes.csv")

labelleft <- labelOptions(noHide = T,
                          direction = "bottom",
                          offset=c(0,-5),
                          opacity=1,
                          style = list(
                            "font-style" = "bold",
                            "font-size" = "20px",
                            "color"="white",
                            "background"="transparent",
                            "border"="none",
                            "box-shadow"="none"))
labelright <- labelOptions(noHide = T,
                           direction = "top",
                           offset=c(0,-5),
                           opacity=1,
                           style = list(
                             "font-style" = "bold",
                             "font-size" = "20px",
                             "color"="white",
                             "background"="transparent",
                             "border"="none",
                             "box-shadow"="none"))

nodesa <- Nodes[c(1,3,5),]
nodesb <- Nodes[c(2,4,6),]

leaflet(nodesa) %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(~ Longitude, ~ Latitude, 
                   radius=0,
                   stroke = FALSE, 
                   fillOpacity = 0.5,
                   label= ~ Lagoon,
                   labelOptions = labelleft) %>% 
  addCircleMarkers(data=nodesb, ~ Longitude, ~ Latitude, 
                   radius=0,
                   stroke = FALSE, 
                   fillOpacity = 0.5,
                   label= ~ Lagoon,
                   labelOptions = labelright) %>%
  addScaleBar() %>% 
  addMiniMap(zoomLevelFixed = 2, 
             centerFixed=c(65, -150))

```


#Blank, zoomable map for labelling in PP, Inkscape etc: SQUARE
```{r blankmap, echo=F, message=F, warnings=F, fig.height=6, fig.width=6}

  
Nodes %>% leaflet() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(~ Longitude, ~ Latitude, 
                   stroke = F, 
                   fillOpacity = 0.0,
                   label= F) %>% 
  addScaleBar() %>% 
  addMiniMap(zoomLevelFixed = 2, 
             centerFixed=c(65, -150))

```

#Blank, zoomable map for labelling in PP, Inkscape etc: WIDE
```{r blankmap_wide, echo=F, message=F, warnings=F, fig.width=11}

Nodes %>% leaflet() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(~ Longitude, ~ Latitude, 
                   stroke = F, 
                   fillOpacity = 0.0,
                   label= F) %>% 
  addScaleBar() %>% 
  addMiniMap(zoomLevelFixed = 2, 
             centerFixed=c(65, -150))

```


